Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-26 paper-ieee-trans.tex
fixed all refs

\bibitem{cmm}
Paulk M., Curtis B., Chrissis M., and Weber V. C.,
Capability maturity model for software,
\emph{Software Engineering Institute},
report CMU/SEI-93-TR-24, ESC--TR-93-177, 1993.

\bibitem{cordis:egee}
\emph{Enabling Grids for E--sciencE (EGEE)} project, European Community Research and
Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/80149\_en.html}
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee2}
\emph{Enabling Grids for E--sciencE--II (EGEE--II)} project, European Community Research and
Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/99189\_en.html}
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee3}
\emph{Enabling Grids for E--sciencE--III (EGEE--III)} project, European Community
Research and Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/87264\_en.html}
[Accessed 4 Jun. 2018].

\bibitem{egee}
F. Gagliardi and M. E. B\'{e}gin,
EGEE -- providing a production quality grid for e-science,
in \emph{2005 IEEE Inter. Symp. on Mass Storage Systems and Technology},
pp. 88-92, 2005.

\bibitem{egee:acceptance-criteria}
\emph{Definition and Documentation of the Revised Software Life--Cycle Process},
Milestone MSA3.4.2, 2010, EGEE--III project.
[Online] Available: \url{https://edms.cern.ch/ui/file/1062487/2/EGEE-III-MSA3.4.2-1062487-v1_4.pdf}
[Accessed 4 Jun. 2018].

\bibitem{glite}
E. Laure et al.,
Programming the Grid with gLite,
\emph{Computational Methods in Science and Technology},
vol. 12(1), pp. 33--45, 2006.

\bibitem{condor}
D. Thain, T. Tannenbaum, M. Livny,
Condor and the Grid,
in \emph{Grid Computing: Making the Global Infrastructure a Reality},
Chapter 11, pp. 63--70, 2002.

\bibitem{etics}
A. Di Meglio, et al.,
ETICS: the international software engineering service for the grid,
in \emph{J. Phys.: Conf. Ser.},
vol. 119, n. 4, 042010, 2008.

\bibitem{cordis:emi}
C. Aiftimiei, et al.,
Towards next generations of software for distributed infrastructures: The European Middleware Initiative,
in \emph{2012 IEEE 8th Inter. Conf. on E-Science},
pp. 1--10, 2012.

\bibitem{iso-9126}
\emph{ISO/IEC 9126 Software Engineering - Product Quality},
International Organization for Standardization.
[Online] Available: \url{https://www.iso.org/standard/22749.html}
[Accessed 4 Jun. 2018].

\bibitem{emi-quality-model}
M Alandes, et al.,
Experiences with Software Quality Metrics in the EMI middleware,
in \emph{J. Phys.: Conf. Ser.}
vol. 396, n. 5, 052003, 2012.

\bibitem{cordis:egi-inspire}
I. Campos Plasencia,
EGI.eu the European grid initiative.
in \emph{4 th Iberian Grid Infrastructure Conf. Proc.},
pp. 5--15, 2010.

\bibitem{egi-ops}
H. Cordier, et al.,
From EGEE Operations Portal towards EGI Operations Portal,
in \emph{Data Driven e-Science (ISGC2010)},
pp. 129--140, 2011.

\bibitem{ggus}
T. Antoni, et al.,
Global grid user support—building a worldwide distributed user support infrastructure,
\emph{J. Phys.: Conf. Ser.},
vol. 119, n. 5, 052002, 2008.

\bibitem{gocdb}
G. Mathieu and J. Casson,
GOCDB4, a New Architecture for the European Grid Infrastructure,
in \emph{Data Driven e-Science (ISGC2010)},
pp. 163--174, 2011.

\bibitem{egi-qc}
\emph{EGI Quality Criteria}.
[Online] Available: \url{https://egi-qc.github.io/}
[Accessed 4 Jun. 2018].

\bibitem{rafi2012}
D. M. Rafi el al.,
Benefits and limitations of automated software testing: Systematic literature review and practitioner survey,
\emph{Proceedings of the 7th International Workshop on Automation of Software Test},
36--42, 2012.

\bibitem{chen2015}
L. Chen,
Continuous delivery: Huge benefits, but challenges too,
\emph{IEEE Software},
vol. 32, no 2, pp. 50--54, 2015.

\bibitem{mario}
M. David et al.,
Validation of Grid Middleware for the European Grid Infrastructure,
\emph{Journal of Grid Computing},
vol. 12, issue 3, pp. 543--558, 2014.

\bibitem{cordis:egi-engage}
\emph{Engaging the EGI Community towards an Open Science Commons (EGI--ENGAGE)}
project, European Community Research and Development Information Service (CORDIS).
[Online] Available: \url{http://cordis.europa.eu/project/rcn/194937\_en.html}
[Accessed 4 Jun. 2018].

\bibitem{cordis:indigo}
Davide Salomoni, et al.,
INDIGO-DataCloud: {A} data and computing platform to facilitate seamless access to e-infrastructures,
\emph{CoRR},
vol. abs/1711.01981, 2018,
[Online] Available: \url{http://arxiv.org/abs/1711.01981}.

\bibitem{indigo-d31}
J. Gomes, et al.,
\emph{Initial Plan for WP3} INDIGO--DataCloud Deliverable 3.1.
[Online] Available: \url{https://www.indigo-datacloud.eu/documents/initial-plan-wp3-d31}
[Accessed 4 Jun. 2018].

\bibitem{sqa-baseline}
Pablo Orviz et al.,
A set of common software quality assurance baseline criteria for research projects,
2017.
[Online] Available: \url{http://digital.csic.es/bitstream/10261/160086/4/CommonSQA-v2.pdf}

\bibitem{disvis}
G.C.P. Van Zundert, A.M.J.J. Bonvin,
DisVis: quantifying and visualizing the accessible interaction space of distance
restrained biomolecular complexes,
\emph{Bioinformatics}, vol. 31, n. 19, pp. 3222--3224, 2015.

\bibitem{powerfit}
G.C.P. Van Zundert, A.M.J.J. Bonvin,
Fast and sensitive rigid--body fitting into cryo--EM density maps with PowerFit,
\emph{AIMS Biophys.}, vol. 2, n. 20150273, 73--87, 2015.

>>>>

\bibitem{cmm}
M. Paulk, B. Curtis, M. Chrissis and V. C. Weber,
``Capability maturity model for software,''
Softw. Eng. Inst.,
Technical Report CMU/SEI-93-TR-024, ESC-TR-93-177, Feb. 1993.
[Online]. Available: \url{https://resources.sei.cmu.edu/asset_files/TechnicalReport/1993_005_001_16211.pdf}.
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee}
\emph{Enabling Grids for E--sciencE (EGEE)} project, European Community Research and
Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/80149\_en.html}.
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee2}
\emph{Enabling Grids for E--sciencE--II (EGEE--II)} project, European Community Research and
Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/99189\_en.html}.
[Accessed 4 Jun. 2018].

\bibitem{cordis:egee3}
\emph{Enabling Grids for E--sciencE--III (EGEE--III)} project, European Community
Research and Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/87264\_en.html}.
[Accessed 4 Jun. 2018].

\bibitem{egee}
F. Gagliardi and M. E. Begin,
``EGEE -- providing a production quality grid for e-science,''
in \emph{2005 IEEE Inter. Symp. Mass Storage Syst. Technol.},
pp. 88--92, Jun. 2005.

\bibitem{egee:acceptance-criteria}
\emph{Definition and Documentation of the Revised Software Life--Cycle Process},
Milestone MSA3.4.2, 2010, EGEE--III project.
[Online]. Available: \url{https://edms.cern.ch/ui/file/1062487/2/EGEE-III-MSA3.4.2-1062487-v1_4.pdf}.
[Accessed 4 Jun. 2018].

\bibitem{glite}
E. Laure \emph{et al.},
``Programming the Grid with gLite,''
\emph{Computational Meth. Sci. Technol.},
vol. 12(1), pp. 33--45, 2006.

\bibitem{condor}
D. Thain, T. Tannenbaum and M. Livny,
``Condor and the Grid,''
in \emph{Grid Computing: Making the Global Infrastructure a Reality},
ch. 11, pp. 63--70, 2003.

\bibitem{etics}
A D Meglio, M-E Begin, P Couvares, E Ronchieri and E Takacs,
``ETICS: the international software engineering service for the grid,''
in \emph{J. Phys.: Conf. Ser.},
vol. 119, no. 4, 042010, 2008.

\bibitem{cordis:emi}
C. Aiftimiei \emph{et al.},
``Towards next generations of software for distributed infrastructures: The European Middleware Initiative,''
in \emph{2012 IEEE 8th Inter. Conf. on E-Science},
Chicago, IL, pp. 1--10, 2012.

\bibitem{iso-9126}
\emph{ISO/IEC 9126 Software Engineering - Product Quality},
International Organization for Standardization.
[Online]. Available: \url{https://www.iso.org/standard/22749.html}.
[Accessed 4 Jun. 2018].

\bibitem{emi-quality-model}
M. Alandes \emph{et al.},
``Experiences with Software Quality Metrics in the EMI middleware,''
in \emph{J. Phys.: Conf. Ser.},
vol. 396, no. 5, 052003, 2012.

\bibitem{cordis:egi-inspire}
I. C. Plasencia,
``EGI.eu the European grid initiative,''
in \emph{4th Iberian Grid Infra. Conf. Proc.},
pp. 5--15, 2010.

\bibitem{egi-ops}
H. Cordier \emph{et al.},
``From EGEE Operations Portal towards EGI Operations Portal,''
in \emph{Data Driven e-Science (ISGC2010)},
pp. 129--140, 2011.

\bibitem{ggus}
T. Antoni \emph{et al.},
``Global grid user support—building a worldwide distributed user support infrastructure,''
\emph{J. Phys.: Conf. Ser.},
vol. 119, no. 5, 052002, 2008.

\bibitem{gocdb}
G. Mathieu and J. Casson,
``GOCDB4, a New Architecture for the European Grid Infrastructure,''
in \emph{Data Driven e-Science (ISGC2010)},
pp. 163--174, 2011.

\bibitem{egi-qc}
\emph{EGI Quality Criteria}.
[Online]. Available: \url{https://egi-qc.github.io/}.
[Accessed 4 Jun. 2018].

\bibitem{rafi2012}
D. M. Rafi \emph{el al.},
``Benefits and limitations of automated software testing: Systematic literature review and practitioner survey,''
in \emph{Proc, 7th Int. Workshop Automation Softw. Test},
36--42, 2012.

\bibitem{chen2015}
L. Chen,
``Continuous delivery: Huge benefits, but challenges too,''
\emph{IEEE Softw.},
vol. 32, no 2, pp. 50--54, 2015.

\bibitem{mario}
M. David \emph{et al.},
``Validation of Grid Middleware for the European Grid Infrastructure,''
\emph{J. Grid Comp.},
vol. 12, no. 3, pp. 543--558, 2014.

\bibitem{cordis:egi-engage}
\emph{Engaging the EGI Community towards an Open Science Commons (EGI--ENGAGE)}
project, European Community Research and Development Information Service (CORDIS).
[Online]. Available: \url{http://cordis.europa.eu/project/rcn/194937\_en.html}.
[Accessed 4 Jun. 2018].

\bibitem{cordis:indigo}
D. Salomoni \emph{et al.},
``INDIGO-DataCloud: A data and computing platform to facilitate seamless access to e-infrastructures,''
\emph{CoRR},
vol. abs/1711.01981, 2018.
[Online]. Available: \url{http://arxiv.org/abs/1711.01981}.
[Accessed 4 Jun. 2018].

\bibitem{indigo-d31}
J. Gomes \emph{et al.},
``Initial Plan for WP3,''
\emph{INDIGO--DataCloud Deliverable 3.1}.
[Online]. Available: \url{https://www.indigo-datacloud.eu/documents/initial-plan-wp3-d31}.
[Accessed 4 Jun. 2018].

\bibitem{sqa-baseline}
Pablo Orviz \emph{et al.},
``A set of common software quality assurance baseline criteria for research projects,''
2017.
[Online]. Available: \url{http://digital.csic.es/bitstream/10261/160086/4/CommonSQA-v2.pdf}.
[Accessed 4 Jun. 2018].

\bibitem{disvis}
G.C.P. Van Zundert and A.M.J.J. Bonvin,
``DisVis: quantifying and visualizing the accessible interaction space of distance
restrained biomolecular complexes,''
\emph{Bioinformatics}, vol. 31, no. 19, pp. 3222--3224, 2015.

\bibitem{powerfit}
G.C.P. Van Zundert and A.M.J.J. Bonvin,
``Fast and sensitive rigid--body fitting into cryo--EM density maps with PowerFit,''
\emph{AIMS Biophys.}, vol. 2, no. 20150273, 73--87, 2015.
